### 2022-04-27 paper1.tex
final submission to graduate college complete!

With the expansion of big data, some computational social science research has
developed extremely innovative methods that have led to groundbreaking results
using reliable sources of big data. As an
example,\citet{blumenstockPredictingPovertyWealth2015} use county-level
cell-phone records to construct the distribution of poverty and wealth in
Rwanda, a country where national surveys and censuses are rare and costly.
In this paper,  \citet{blumenstockPredictingPovertyWealth2015} put in an effort to 
investigate the criterion validity of their measure; that is, they investigate 
how well an \textit{operationalization} of a specific construct is able to 
predict a \textit{theoretical representation} of the construct — the criterion. 
Investigating the criterion validity in their paper demonstrate that their use
of the cell phone data creates a reliable and valid construct. 
Few other social science papers utilizing big data dig into the criterion
validity of their metrics to this extent;even fewer publications focus on
methodological guidelines of how to use sources of big data \citep[For
exceptions, see ][]{asseoTrackingCOVID19Using2020,
stilesAssessingCriterionValidity2018}. However, research has shown the small
adjustments to an algorithm or metric may void any research insight we can pull
from such data \citep{lazerParableGoogleFlu2014}.

>>>>

With the expansion of big data, some computational social science research has
developed extremely innovative methods that have led to groundbreaking results
using reliable sources of big data. As an
example,\citet{blumenstockPredictingPovertyWealth2015} use county-level
cell-phone records to construct the distribution of poverty and wealth in
Rwanda, a country where national surveys and censuses are rare and costly.
In this paper,  \citet{blumenstockPredictingPovertyWealth2015} put in an effort to 
investigate the criterion validity of their measure; that is, they investigate 
how well an \textit{operationalization} of a specific construct is able to 
predict a \textit{theoretical representation} of the construct — the criterion. 
Investigating the criterion validity in their paper demonstrate that their use
of the cell phone data creates a reliable and valid construct. 
Few other social science papers utilizing big data dig into the criterion
validity of their metrics to this extent; even fewer publications focus on
methodological guidelines of how to use sources of big data \citep[For
exceptions, see ][]{asseoTrackingCOVID19Using2020,
stilesAssessingCriterionValidity2018}. However, research has shown the small
adjustments to an algorithm or metric may void any research insight we can pull
from such data \citep{lazerParableGoogleFlu2014}.
